\documentclass[letterpaper, 11 pt, conference]{ieeeconf}

\IEEEoverridecommandlockouts
\overrideIEEEmargins

% The following packages can be found on http:\\www.ctan.org
\usepackage{graphics} % for pdf, bitmapped graphics files
%\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
%\usepackage{amsmath} % assumes amsmath package installed
%\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{float}
\usepackage{caption}
\usepackage{listings}
\usepackage{color}
\usepackage{geometry}
\geometry{a4paper}
\usepackage[english]{babel}
\selectlanguage{english}
\usepackage[utf8]{inputenc}

\usepackage{subcaption}
\usepackage{amssymb}
\usepackage{authblk}
\usepackage{graphicx}

\title{Job Delegation}
\author{Bradley Wood$^{1}$, Brock Watling$^{2}$, Zachary Winn$^{3}$, Daniel Messiha$^{4}$}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstdefinelanguage{Kotlin}{
comment=[l]{//},
commentstyle={\color{gray}\ttfamily},
emph={delegate, filter, first, firstOrNull, forEach, lazy, map, mapNotNull, println, return@},
emphstyle={\color{OrangeRed}},
identifierstyle=\color{black},
keywords={abstract, actual, async, callback, delegate, as, as?, break, by, class, companion, continue, data, do, dynamic, else, enum, expect, false, final, for, fun, get, if, import, in, interface, internal, is, null, object, override, package, private, public, return, set, super, suspend, this, throw, true, try, typealias, val, var, vararg, when, where, while},
keywordstyle={\color{NavyBlue}\bfseries},
morecomment=[s]{/*}{*/},
morestring=[b]",
morestring=[s]{"""*}{*"""},
ndkeywords={@Deprecated, @JvmField, @JvmName, @JvmOverloads, @JvmStatic, @JvmSynthetic, Array, Byte, Double, Float, Int, Integer, Iterable, Long, Runnable, Short, String},
ndkeywordstyle={\color{BurntOrange}\bfseries},
sensitive=true,
stringstyle={\color{ForestGreen}\ttfamily},
}

\lstset{frame=tb,
language=Kotlin,
aboveskip=3mm,
belowskip=3mm,
showstringspaces=false,
columns=flexible,
basicstyle={\small\ttfamily},
numbers=none,
numberstyle=\tiny\color{gray},
keywordstyle=\color{blue},
commentstyle=\color{dkgreen},
stringstyle=\color{mauve},
breaklines=true,
breakatwhitespace=true,
tabsize=3
}

\begin{document}

    \maketitle
    \thispagestyle{empty}
    \pagestyle{empty}

    \input{sections/abstract.tex}

    \input{sections/introduction.tex}

    \input{sections/related.tex}

    \input{sections/features.tex}

    \input{sections/implementation.tex}

    \input{sections/failure.tex}

    \input{sections/architecture.tex}

    \input{sections/overhead.tex}

    \input{sections/practical.tex}

    \input{sections/conclusion.tex}

    \addtolength{\textheight}{-12cm}

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \begin{thebibliography}{99}

        \bibitem{jvm}
        T. Lindholm, F. Yellin, G. Bracha and A. Buckley, docs.oracle.com, 2018. [Online].
        Available: https://docs.oracle.com/javase/specs/jvms/se8/jvms8.pdf.

        \bibitem{asm}
        Eric Bruneton, "ASM Developer Guide." [Online].
        Available: https://asm.ow2.io/developer-guide.html.

        \bibitem{kotlinRef}
        [Online].
        Available: https://kotlinlang.org/docs/kotlin-docs.pdf.

        \bibitem{hadoop}
        "Apache Hadoop", Hadoop.apache.org, 2018. [Online].
        Available: https://hadoop.apache.org/.

        \bibitem{migration}
        Flatworldsolutions.com. (2018).
        Cloud Migration Advantages & Disadvantages - Flatworld Solutions.
        [online] Available at: https://www.flatworldsolutions.com/IT-services/articles/cloud-migration-advantages-disadvantages-risk-mitigation.php

        \bibitem{hazelcast}
        "What Is Hazelcast? - Developer.com", Developer.com, 2018.
        [Online].
        Available: https://www.developer.com/java/data/what-is-hazelcast.html.

    \end{thebibliography}


\end{document}
