\section{OVERHEAD}\label{sec:overhead}

The RMD platform provides two forms of significant overhead.
Advanced users can limit the effects of initiation and network
overhead by following the best practices.
It is not easy to talk about the efficiency of the platform
because it is highly dependent on the implementation requirements
of the user specified jobs.

\subsection{Initialization Overhead}\label{subsec:initializationOverhead}

Initialization overhead occurs during the first call to a delegate job.
Firstly, RMD must locate and connect to external load balancers and
job servers.
Concurrently, RMD will attempt to dynamically determine the callsite
of your job, and determine its dependencies.
There are two determinants of this overhead, including the
number of dependencies that your job depends on, and the network
speed.
By limiting the number of dependencies used by your job,
you decrease the graph traversal time, and limit the amount
of the code that must be migrated through the network.
Therefore it is recommended to make extensive use of the Java and Kotlin
standard libraries and limit the use of other external libraries.
Classes that are part of the standard libraries do not need to be migrated
to the server, as they already exist on the server side.
This callsite and dependency information is cached so that such calculations
do not need to be performed again.


\subsection{Job Request Overhead}\label{subsec:networkOverhead}

Each job request has three forms of overhead after the migration
process has been completed.
Firstly, the job must be looked up in the cache to verify
that the code exists on the external server.
Next, the job's function parameters must be serialized, which
is usually not a cause of large overhead. However, it could be a problem
if your job parameters consume a large amount of data.
The transmission phase is usually the largest source of overhead,
and often dwarfs the other forms of overhead.
It is recommended not to write jobs that depend on large amounts
of input data, due to the overhead caused by each job request.
Such job requests may be acceptable for your application if they do
not need to be executed very often.
